---
# title: "Detailed Example"
author: "Sharon"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Detailed Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Specific test functions


## Load the koboLoops Package

```{r, results='hide', message=FALSE,warning=FALSE,error=FALSE}
library("koboloops")
```

## Example data frame

Here we create some fake data for illustration purposes.
It is not important to understand this; we keep it in so you can run the example yourself if you like.
There are two datasets.

The parent one contains:

- variable `uuid`: values must be unique
- variable `age`: values between 30 and 60
- variable `parent_gender`

The child contains:

- variable `parent_uuid`: should be number among the uuid of the parent dataset
- variable `age`: values between 1 and 18
- variable `child_gender` just some numbers, but the column header indicates this is potentially sensitive


```{r}
parent <- data.frame(uuid=1:10, age_parent=sample(30:60,10,replace = T),parent_gender=sample(c("F","M"),10,replace = T))

child <- data.frame(parent_uuid=sample(1:10,20,replace = T), age_child=sample(1:18,20,replace=T), child_gender=sample(c("F","M"),20,replace = T))
```

## Affect parent age to each child


```{r,eval=F}
family <- add_parent_to_loop(child,parent,uuid.name.loop = "parent_uuid",uuid.name.parent = "uuid",c("age_parent"))
family
```

run `?add_parent_to_loop` for details.

## Affect all parent information to each child

We affect to the parent the average ages of the children.

```{r}
variable.to.add = c(mean_of_child_age="age_child")
```

```{r,eval=F}
family <- affect_loop_to_parent(child, parent,aggregate.function = mean , variable.to.add)
family
```

run `?affect_loop_to_parent` for details.



